Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-14 paper/abstraction/paper.tex
describe list comprehension syntax in paper

\begin{figure*}[t!]
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Policy Automata}{}
  \vspace{1em}
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{N1}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 1 DFA};
    \end{tikzpicture}
    ~~~~~
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{N2}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 2 DFA};
    \end{tikzpicture}%
  \end{minipage}
  %
  ~~~~~~
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Concrete Topology}{}
    \vspace{1em}
    \includegraphics[width=.62\columnwidth]{figures/topology-con}
  \end{minipage}%
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Abstract Topology}{}
    \vspace{1em}
    \includegraphics[width=.505\columnwidth]{figures/topology-abs}
  \end{minipage}%

@@

\newcommand{\inferencetwo}[1]{
    \node[draw, anchor=west] at (#1 + 2, 1.25) {$e_i > 0$};
    \node[] at (#1 + .46, 1.25 + 2.5) {\textbf{I-striping}};
    \node at (#1 - 1 - .11, .6) {$e_1$};
    \node at (#1 + .11, 1.5) {$e_2$};
    \node at (#1 + 2 + .11, .6) {$e_3$};
    \node at (#1 + .11 + .8, 1.5) {$e_4$};
    \node at (#1 - 1, -.8) {L$_m(j,k)$};
    \node at (#1 +. 5, 2.9) {S$_n(min(j*k,g),1)$};
    \node at (#1 + 2, -.8) {S$_o\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
    \node at (#1, 3.3) {};
    \draw [] (#1 + .5, 2.01) circle [radius=0.4] node {$n$};
    \draw [] (#1 - 1, 0) circle [radius=0.4] node {$m$};
    \draw [] (#1 + 2, 0) circle [radius=0.4] node {$o$};
    \draw [->] (#1 - 1, .4) -- (#1 + .5, 2 - .4);
    \draw [<-] (#1 + 2, .4) -- (#1 + .5, 2 - .4);
}

@@

  \vspace*{1em}
  \begin{minipage}[t]{\linewidth}%
  \begin{tikzpicture}
    % \inference{0}{L$(j,k)$}{$e_i > 0$}{S$(min(j*k,g),1)$}{I-out3}{$e_1$}{$e_2$}
    \inferencetwo{0}
    \node[anchor=west] at (1,2.2) {where $g \geq n-\dfrac{(m-j)*e_1}{e_2}$};
    \inferencelocal{6.5}{.4}
    \inferenceglobal{12}{.4}
  \end{tikzpicture}
  \end{minipage}

@@

For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 appears in two PG nodes: $(S1,1,0)$ and $(S1,0,1)$. These nodes have two peers that can send them messages in the PG: $(N1,0,0)$ and $(N2,0,0)$. Therefore, S1 will allow advertisements from both peer $N1$ and peer $N2$. If S1 uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ to the advertisement before sending this to its neighbors A1 and A2. If S1 uses a path advertised from neighbor N2, then it will add the tag $(0,1)$ instead. Similarly, router A1 appears in two separate PG nodes. It will allow advertisements from S1 if they either have the $(1,0)$ tag or the $(0,1)$ tag attached. In either case, it will not modify the tag before exporting the route to its neighbors.

@@

  %\vspace{1em}%
  \begin{minipage}[t]{.47\linewidth}
  \hdr{mBGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     d    &   & & \textit{integer} \\
     c    &   & & \textit{community} \\
     l    &   & & \textit{location} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     mbgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{mbgp policy} \\%
  \end{array} \]%%

@@

  \vspace{1em}
  \hrulefill%
  \vspace{-.8em}
  \caption{mBGP syntax (left), and compilation from product graphs (right).}
  \label{fig:concretization}
  \vspace{-.8em}
\end{figure*}%

@@

\begin{defn}
Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$. Intuitively $m \geq_{rank} n$ means that paths ending at node $m$ have higher automata rank and are thus no better than paths ending at $n$.
%
\end{defn}
\noindent
%

%\begin{defn}
The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge. That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.
%\end{defn}
%
For example, in the concrete PG we would have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.

@@

More specifically, we say that $m \leq n$ if $m \geq_{rank} n$ and for every transition $n\overset{l}{\rightarrow}n'$ from PG node $n$ there exists a transition $m\overset{l}{\rightarrow}m'$ from $m$ and $m' \leq n'$.
%
Intuitively, the $m \leq n$ relation means advertisements received for node $m$ can safely be preferred over those received for node $n$ after accounting for the network-wide impact of the choice. For example in Figure~\ref{fig:example-compilation}, S1 can receive advertisements in two different contexts ($(S1,1,0)$ and $(S1,0,1)$) and must choose between messages received in these different contexts. Advertisements are preferred in state $(S1,1,0)$ because it results in a better path for S1 ($(S1,0,1) \geq_{rank} (S1,1,0)$) and downstream routers such as A1 will also obtain paths no worse than if S1 had choosen $(S1,1,0)$ instead. The policy is guaranteed to be safe from failures because if a link fails in the topology, then $m \leq n$ will still hold since any transition that becomes unusable for $m$ also becomes unusable for $n$. That is $m \leq n$ before the failure implies $m \leq n$ after the failure.

@@

Figure~\ref{fig:concretization} (right) defines compilation from \sysname to \mbgp. It proceeds by compiling constraints $p_i$ in the original \sysname policy to a tuple of: the predicate $t_i$, the product graph $PG_i$, and the preference function $pref_i$. These tuples are passed the the $\mathrm{compile}_\mathrm{mBGP}$ function, along with the network topology $G$. For each internal router in the topology $l$, and each predicate $t_i$ in the \sysname policy, compilation goes through each node $m$ for $l$ in $PG_i$, and groups the inbound neighbors of $m$ by tag ($q_n$) into sets ($in$). It allows imports from these neighbors before exporting to the outbound neighbors of $m$. The local preference for these imports is given by $\mathrm{pref}_i(m)$.

@@

The top part of Figure~\ref{fig:analysis-precision} shows the results for common real-world settings: tree-based topologies coupled with valley-free routing.
We consider four variants of tree topologies: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault-tolerant fat tree~\cite{f10-fattree}, and VL2~\cite{vl2-fattree}. These variants differ in the number of tiers and the connectivity pattern between roles. For each, we use a tiered abstraction similar to that in our example (\S\ref{sec:overview}) and parameterize over the number of pods, which can be scaled to allow expansion. We report precision of both analyzing reachability and computing the number of disjoint paths, and we report if \sysname is precise for all pairs of abstract nodes or only some of them. We record a check when the analysis is precise and a \Conserv{} when the analysis is conservative. %"All pairs" precision implies "some pairs" precision, but not the other way around.

@@

\begin{figure}[t!]
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/Fattree-analysis-time.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/backbone-analysis-time.png}} \\
  \vspace{-.6em}
  \caption{Abstract Synthesis Time by Phase. \label{fig:abstract-breakdown}}
  \vspace{-1em}
\end{figure}

>>>>

\begin{figure*}[t!]
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Policy Automata}{}
  \vspace{1em}
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{N1}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 1 DFA};
    \end{tikzpicture}
    ~~~~~
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{N2}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 2 DFA};
    \end{tikzpicture}%
  \end{minipage}
  %
  ~~~~~~
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Concrete Topology}{}
    \vspace{1em}
    \includegraphics[width=.60\columnwidth]{figures/topology-con}
  \end{minipage}%
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Abstract Topology}{}
    \vspace{1em}
    \includegraphics[width=.49\columnwidth]{figures/topology-abs}
  \end{minipage}%

@@

\newcommand{\inferencetwo}[1]{
    \node[draw, anchor=west] at (#1 + 2, 1.25) {$e_i > 0$};
    \node[] at (#1 + .46, 1.25 + 2.5) {\textbf{I-striping}};
    \node at (#1 - 1 - .11, .6 + .2) {$e_1$};
    \node at (#1 + .11, 1.5 + .2) {$e_2$};
    \node at (#1 + 2 + .11, .6 + .2) {$e_3$};
    \node at (#1 + .11 + .8, 1.5 + .2) {$e_4$};
    \node at (#1 - 1, -.8 + .2) {L$_m(j,k)$};
    \node at (#1 +. 5, 2.9 + .2) {S$_n(min(j*k,g),1)$};
    \node at (#1 + 2, -.8 + .2) {S$_o\big( min(j, g *\frac{e_4}{e_3}),1\big)$};
    \node at (#1, 3.3 + .2) {};
    \draw [] (#1 + .5, 2.01 + .2) circle [radius=0.4] node {$n$};
    \draw [] (#1 - 1, 0 + .2) circle [radius=0.4] node {$m$};
    \draw [] (#1 + 2, 0 + .2) circle [radius=0.4] node {$o$};
    \draw [->] (#1 - 1, .4 + .2) -- (#1 + .5, 2 - .4 + .2);
    \draw [<-] (#1 + 2, .4 + .2) -- (#1 + .5, 2 - .4 + .2);
}

@@

  \vspace*{.2em}
  \begin{minipage}[t]{\linewidth}%
  \begin{tikzpicture}
    % \inference{0}{L$(j,k)$}{$e_i > 0$}{S$(min(j*k,g),1)$}{I-out3}{$e_1$}{$e_2$}
    \inferencetwo{0}
    \node[anchor=west] at (1,2.2) {where $g \geq n-\dfrac{(m-j)*e_1}{e_2}$};
    \inferencelocal{6.5}{.4}
    \inferenceglobal{12}{.4}
  \end{tikzpicture}
  \end{minipage}

@@

For example, in the concrete PG in Figure~\ref{fig:example-compilation}, router S1 appears in two PG nodes: $(S1,1,0)$ and $(S1,0,1)$. These nodes have two peers that can send them messages: $(N1,0,0)$ and $(N2,0,0)$. Therefore, S1 will allow advertisements from both peer $N1$ and peer $N2$. If S1 uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ to the advertisement before sending this to its neighbors A1 and A2. If S1 uses a path advertised from neighbor N2, then it will add the tag $(0,1)$ instead. Similarly, router A1 appears in two separate PG nodes. It will allow advertisements from S1 if they either have the $(1,0)$ tag or the $(0,1)$ tag attached. In either case, it will not modify the tag before exporting the route to its neighbors.

@@

  %\vspace{1em}%
  \begin{minipage}[t]{.47\linewidth}
  \hdr{mBGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     d    &\in& \textit{Integers} & \\
     c    &\in& \textit{Communities} & \\
     l    &\in& \textit{Topology Locations} & \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     mbgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{mbgp policy} \\%
  \end{array} \]%%

@@

  \vspace{1em}
  \hrulefill%
  \vspace{-.8em}
  \caption{mBGP syntax (left), and compilation from product graphs (right).}
  \label{fig:concretization}
  \vspace{-.4em}
\end{figure*}%

@@

\begin{defn}
Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\Topo{m} = \Topo{n}$ and either $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$.
%
\end{defn}
\noindent
%
Intuitively $m \geq_{rank} n$ means that paths ending at node $n$ have lower automata rank and are thus better than paths ending at $m$.
%\begin{defn}
The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge. That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.
%\end{defn}
%
For example, in the concrete PG we have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.

@@

More specifically, we say that $m \leq n$ if $m \geq_{rank} n$ and for every transition $n\overset{l}{\rightarrow}n'$ from PG node $n$ there exists a transition $m\overset{l}{\rightarrow}m'$ from $m$ and $m' \leq n'$.
%
If $m \leq n$, then advertisements received for node $m$ can safely be preferred over those received for node $n$ after accounting for the network-wide impact of the choice. For example in Figure~\ref{fig:example-compilation}, S1 can receive advertisements in two different contexts ($(S1,1,0)$ and $(S1,0,1)$) and must choose between messages received in these different contexts. Advertisements are preferred in state $(S1,1,0)$ because it results in a better path for S1 ($(S1,0,1) \geq_{rank} (S1,1,0)$) and downstream routers such as A1 will also obtain paths no worse than if S1 had choosen $(S1,1,0)$ instead. The policy is guaranteed to be safe from failures because if a link fails in the topology, then $m \leq n$ will still hold since any transition that becomes unusable for $m$ also becomes unusable for $n$. That is $m \leq n$ before the failure implies $m \leq n$ after the failure.

@@

Figure~\ref{fig:concretization} (right) defines compilation from \sysname to \mbgp. It proceeds by compiling constraints $p_i$ in the original \sysname policy to a tuple of: the predicate $t_i$, the product graph $PG_i$, and the preference function $pref_i$. These tuples are passed the the $\mathrm{compile}_\mathrm{mBGP}$ function, along with the network topology $G$. For each internal router in the topology $l$, and each predicate $t_i$ in the \sysname policy, compilation goes through each node $m$ for $l$ in $PG_i$, and groups the inbound neighbors of $m$ by tag ($q_n$) into sets ($in$). It allows imports from these neighbors before exporting to the outbound neighbors of $m$. The local preference for these imports is given by $\mathrm{pref}_i(m)$. We build configs using list-comprehension notation. For instance, $[~ l \rightarrow rc ~\vert~ l \in V, p(l,rc) ~]$ denotes the \mbgp policy $l_1 \rightarrow rc_{1},...,l_k \rightarrow rc_{k}$ where each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use $\mathit{append}$ to denote sequence concatenation.%

@@

The top part of Figure~\ref{fig:analysis-precision} shows the results for common real-world settings: tree-based topologies coupled with valley-free routing.
We consider four variants of tree topologies: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault-tolerant fat tree~\cite{f10-fattree}, and VL2~\cite{vl2-fattree}. These variants differ in the number of tiers and the connectivity pattern between roles. For each, we use a tiered abstraction similar to that in our example (\S\ref{sec:overview}) and parameterize over the number of pods, which can be scaled for expansion. We report precision of both analyzing reachability and disjoint paths, and we report if \sysname is precise for all pairs of abstract nodes or only some of them. We record a check when the analysis is precise and a \Conserv{} when the analysis is conservative.

@@

\begin{figure}[t!]
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/Fattree-analysis-time.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/backbone-analysis-time.png}} \\
  \vspace{-.6em}
  \caption{Abstract Synthesis Time by Phase. \label{fig:abstract-breakdown}}
  \vspace{-.4em}
\end{figure}
